Make any stupid plot you want

### 2021-02-16 draft/sections/math.tex
more math rewording

can express continuous functions \& not just discrete points
Visualization is generally thought of as structure preserving maps from data into graphics, and in this section we formally define that structure and how it is preserved via equivariant maps. We can then specify that a faithful visual mapping is structure preserving, and apply these constraints to visualizations we may want to develop or implement. We model the data, visual characteristic, and graphic stages of visualization, shown in figure~\ref{fig:artist_stages}, as topological structures that encapsulate types of variables and continuity; by doing so we can develop implementations that keep track of both in ways that let us distribute computation while still allowing assembly and dynamic update of the graphic.

>>>>

As discussed in the introduction, visualization is generally defined as structure preserving maps from data into graphic representation. In order to formalize this statement, we describe the connectivity of the records using topology and define the structure on the components in terms of the monoid actions on the component types. By formalizing structure in this way, we can evaluate the extent to which a visualization preserves the structure of the data it is representing and build structure preserving visualization tools.

We model the data, visual characteristic, and graphic stages of visualization, shown in figure~\ref{fig:artist_stages}, as topological structures that encapsulate types of variables and continuity; by doing so we can develop implementations that keep track of both in ways that let us distribute computation while still allowing assembly and dynamic update of the graphic.
